A meta-analysis of mental rotation ability in the first years of life

### 2022-04-08 code/analysis.Rmd
Include Egger test and correct funnel inputs

# Three-level model
res_mv <- rma.mv(
  yi, vi,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_mv)
forest(res_mv)
funnel(res_mv, main = "Standard Error")

@@

# Meta-regression with age
res_age <- rma.mv(
  yi, vi,
  mods = ~age_months,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_age)
forest(res_age)

# Meta-regression with gender
res_gender <- rma.mv(
  yi, vi,
  mods = ~female_percent,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_gender)
forest(res_gender)
funnel(res_age, main = "Standard Error")

>>>>

# Three-level model
res_mv <- rma.mv(
  yi, vi,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_mv)
forest(res_mv)
funnel(res_mv, main = "Standard Error")
egger=regtest(x=res_mv$yi, vi=res_mv$vi, sei=res_mv$sei,model='lm',predictor='sei')
print(egger)

@@

# Meta-regression with age
res_age <- rma.mv(
  yi, vi,
  mods = ~age_months,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_age)
forest(res_age)
funnel(res_age, main = "Standard Error")

# Meta-regression with gender
res_gender <- rma.mv(
  yi, vi,
  mods = ~female_percent,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_gender)
forest(res_gender)
funnel(res_gender, main = "Standard Error")
